\documentclass{../cs195u}

\usepackage{url}

\asgn{Platformer 3}
\due{March 8, 2021}

\begin{document}
 \section*{Introduction}

In this assignment you will add AI functionality to your engine.

 \section*{Directions}
  
First, you will create a graph from a navmesh stored in an obj file. Next, you will implement pathfinding on the navmesh with the A* algorithm. You will also implement behavior trees. You can improve your pathfinding by implementing the Funnel Algorithm for extra credit.

  \section*{Design Check}
  \begin{itemize}
   \item What is the purpose of the heuristic function in the A* algorithm? What heuristic function will you use?
   \item How do the composite nodes in a behavior tree work?
   \item Give an example of how a blackboard can be used to extend the functionality of behavior trees.
   \item How will you design your action and condition nodes?
  \end{itemize}

  \section*{Engine Requirements}
  \begin{itemize}
    \item Engine has an A* implementation
    \item An AISystem/AIComponent using behavior trees
    \begin{itemize}
    	\item BTNode (virtual)
	\item BTStatus (enum)
	\item Selector
	\item Sequence
	\item Action (virtual)
	\item Condition (virtual)
	\item Blackboard (minimally, a map of strings to anything)
    \end{itemize}
 \end{itemize}
 
 \section*{Game Requirements}
  \begin{itemize}
    \item AI-controlled entity traverses navmesh to some goal (such as the player position)
    \item Basic behavior tree controlling a gameobject
   \end{itemize}

 \section*{Handing In}
Hand in the entire directory tree for your project, including both your engine and game code. You must also include a README file that describes how to verify each requirement, and an INSTRUCTIONS file that describes how to play your game. To hand in, run \texttt{cs195u\_handin platformer3} from the top level directory of your project (which should be where your Qt pro file is). \textbf{Please do not hand in the build files from your project.}

\end{document}
