\documentclass{cs195u}
\usepackage{hyperref}

\misc{Collaboration Policy}
\docdate{Spring 2021}

\begin{document}
 \textbf{Please read and then sign the \href{https://forms.gle/xv71JEBsCUViSGiB6}{form}. You will not receive credit for assignments until you return this document.}
 
 This policy covers all course material and assignments unless otherwise stated. As a reminder, Brown University has an Academic Code that includes a section on Respect for the Integrity of the Academic Process, which requires that all written work must be your own. This is especially important in this class, since grades are determined solely by performance on written projects.
 
 \begin{itemize}
  \item Course material information and documentation may be discussed with anyone.
  \item Assignments may be discussed with the other CS1950U students.
  \begin{itemize}
   \item Discussions may make use of a whiteboard or paper.
   \item You MAY NOT take notes away from these discussions.
   \item Discussions MAY NOT include writing or debugging code.
  \end{itemize}
  \item Implementation code MAY NOT be shown to anyone other than course staff.
  \begin{itemize}
   \item At any time, you may show others your implementation running windowed or fullscreen, but you may not discuss specific debugging details about your code while doing so.
   \item You do not need to hide your screen from anyone, but you should not attempt to show your code to anyone and you may not look at other students' screens with the intent to look at their code.
   \item Final project group members, once final project groups are confirmed, may freely share all the code they have written throughout the semester with each other.
   \item These restrictions remain in effect even after assignments are due.
  \end{itemize}
  \item For some assignments, the TAs may provide graphical and/or textual assets.
  \begin{itemize}
   \item You may choose to use your own assets.
   \item You may share assets you have created and you may collaborate with other CS1950U students in creating assets.
  \end{itemize}
  \item When in doubt, ask a member of the course staff whether a type of communication is allowed or disallowed.
 \end{itemize}
 
\end{document}
